Windowed Developer Topic Analysis

### 2009-03-29 lda-paper.tex
minor changes
postgresql

We extracted the repositories of: MySQL, PostGreSQL, MaxDB and
Firebird.

@@

>>>>

We extracted the repositories of: PostGreSQL, MaxDB and
Firebird.

@@

PostgreSQL did not have many trends with two or more topics, but it
did have one large mega-trend which stretched across most of its
existence. Much of the mega-trend consisted of stop words but it did
include topics which had words such as patch, fix, update.

The second largest topic was interesting because it dealt changes from
1998, from developers using Central Europe Time (CEST), the two
notable tokens were 1998 and CEST. These changes seem to be patches
submitted by one particular developer who used that timezone.

The third largest trend seemed to be about copying and moving files
between branches as it referenced the old branch. This is a side
effect of the programmers manually recording such a merge across
branches because CVS cannot.
